---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "rmd_files/README-"
)
```

# jackknife version 0.1.0 (RED JACK)

The jackknife package implements jackknife method of estimating standard errors.

The corresponding reference here

[The Jackknife and the Bootstrap for eneral Stationary Observations](https://www.jstor.org/stable/pdf/2241719.pdf)


## How to install

You can install the development version from GitHub by running
```{r install2, eval=F}
devtools::install_github("yukai-yang/jackknife")
```
provided that the package "devtools" has been installed beforehand.




After installing the package, you need to load (attach better say) it by running the code
```{r attach}
library(jackknife)
```

You can take a look at all the available functions and data in the package
```{r contents}
ls( grep("jackknife", search()) ) 
```

## Example

let us define the weights for deleting or downweighting the blocks:

```{weight}
vw1 = 1
vw2 = c(0.25,0.75,1,0.75,0.25)
```

Then we simulate data from the AR(1) model
```r{ar1}
# the AR(1) model
iN = 100
mdl <- list(ar = c(0.8))
vx <- arima.sim(model=mdl, iN)
```

### First order autocorrelation

The first order autocorrelation is a linear statistic. We define the corresponding T and delta function below.
```r{auto}
# for first order autocorrelation
# dfunc vec 2, y_t and y_t-1
dfunc <- function(yy, my, vy) return(prod(yy - my)/vy)

tfunc <- function(rho, my, vy) return(rho)
```

We do the jackknife for the first kind of weights:
```r{jack1}
# results
ret = jackknife(as.vector(vx), tfunc, dfunc, im=2, vw=vw1, my=mean(vx), vy=var(vx))
ret
```

Then the second
```r{jack2}
ret = jackknife(as.vector(vx), tfunc, dfunc, im=2, vw=vw2, my=mean(vx), vy=var(vx))
ret
```

Compare them with the autocorrelation function.
```r{acf}
# acf
tmp = acf(vx)
tmp
```

### OLS estimator

The OLS estimator is also a linear statistic. We define the corresponding T and delta function below.
```r{para}
# for estimator of the AR(1)
dfunc <- function(yy, inv_xx) return(c(inv_xx %*% rbind(1, yy[1]) * yy[2]))

tfunc <- function(rho, inv_xx) return(rho)
```

We also need some additional arguments:
```r{inv}
inv_xx = cbind(1,vx[1:(length(vx)-1)])
inv_xx = chol2inv(chol(crossprod(inv_xx)/(length(vx)-1)))
```

The results
```r{res1}
# results
ret = jackknife(as.vector(vx), tfunc, dfunc, im=2, vw=vw1, inv_xx=inv_xx)
ret
```

```r{res2}
ret = jackknife(as.vector(vx), tfunc, dfunc, im=2, vw=vw2, inv_xx=inv_xx)
ret
```


